No Title

### 2017-10-26 paper/paper.tex
caption
+1 caption

\begin{figure*}
\centering
\includegraphics[width=0.32\textwidth]{scatter_random_ranked_ba_ratio.pdf}
\includegraphics[width=0.32\textwidth]{scatter_ranked_ba_ratio.pdf}
\includegraphics[width=0.32\textwidth]{scatter_norm_ba_ratio.pdf}
\caption{Same layout as in Figure \ref{fig:scatter_width}. 
Ths time for the $b/a$ axis ratio.
\label{fig:scatter_ba_ration}}
\end{figure*}

\begin{figure*}
\centering
\includegraphics[width=0.32\textwidth]{scatter_random_ranked_mu.pdf}
\includegraphics[width=0.32\textwidth]{scatter_ranked_mu.pdf}
\includegraphics[width=0.32\textwidth]{scatter_norm_mu.pdf}
\caption{Basic characteristics for the MW and M31 satellite systems
\label{fig:lg_scatter}}
\end{figure*}

>>>>

\begin{figure*}
\centering
\includegraphics[width=0.32\textwidth]{scatter_random_ranked_ba_ratio.pdf}
\includegraphics[width=0.32\textwidth]{scatter_ranked_ba_ratio.pdf}
\includegraphics[width=0.32\textwidth]{scatter_norm_ba_ratio.pdf}
\caption{Same layout as in Figure \ref{fig:scatter_width}. 
This time for the $b/a$ axis ratio. In this case both the MW and M31
are consistent with the results of a spherical distribution and the
simulations. 
\label{fig:scatter_ba_ration}}
\end{figure*}

\begin{figure*}
\centering
\includegraphics[width=0.32\textwidth]{scatter_random_ranked_mu.pdf}
\includegraphics[width=0.32\textwidth]{scatter_ranked_mu.pdf}
\includegraphics[width=0.32\textwidth]{scatter_norm_mu.pdf}
\caption{Same layout as in Figure \ref{fig:scatter_width}. 
This time for $\mu$ the absolute value of the dot product between the
vector connecting the main galaxies and the vector perpendicular to
the satellite plane.
In this case both the MW and M31 show a strong alignment.
Apparently this result is outside the expectations from the
simulations and atypical compared to the spherical results. 
However, this is not the case. The $\mu$ distributions in the
randomization and the simulation are consistent with a uniform
distribution.
Under such circumstances the result of $\mu\approx 1$ is as likely as
any other result.
\label{fig:scatter_mu}}
\end{figure*}
